partial: An R Package for Creating Partial Dependence Plots

### 2016-07-14 manuscript/greenwell.tex
minor updates

\abstract{
Complex predictive models (e.g., neural networks, random forests, and support vector machines) offer much promise in the world of data analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g. multiple linear regression). Unfortunately though, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots offer a simple solution. Partial dependence plots offer low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from complex black box models like support vector machines or neural networks or constructing simpler parsimonious models on newly obtained data. 
}

@@

In higher dimensions, plotting the convex hull is more informative; it outlines the region of the predictor space that the model was trained on. When \code{convex.hull = TRUE}, the convex hull of the first two dimensions of $\boldsymbol{z}_s$ (i.e., the first two variables supplied to \code{pred.var}) is added to the plot. Over interpreting the partial dependence plot outside of this region can be dangerous. The right side of Figure~\ref{fig:partial_extrap} was produced using:
\begin{example}
plotPartial(pd.lstat.rm, convex.hull = TRUE, training.data = boston)
\end{example}

>>>>

\abstract{
Complex predictive models (e.g., neural networks, random forests, and support vector machines) offer much promise in the world of data analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g. multiple linear regression). Unfortunately, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots (PDPs) offer a simple solution. Partial dependence plots are low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from complex black box models like support vector machines or neural networks or constructing simpler parsimonious models on newly obtained data.
}

@@

In higher dimensions, plotting the convex hull is more informative; it outlines the region of the predictor space that the model was trained on. When \code{convex.hull = TRUE}, the convex hull of the first two dimensions of $\boldsymbol{z}_s$ (i.e., the first two variables supplied to \code{pred.var}) is added to the plot; alternatively, you can set \code{convex.hull = TRUE} in the call to \code{partial}, in which case only the region within the convex hull of the first two variables is plotted. Over interpreting the partial dependence plot outside of this region can be dangerous. The right two displays in Figure~\ref{fig:partial_extrap} were produced, respectively, using:
\begin{example}
plotPartial(pd.lstat.rm, convex.hull = TRUE, training.data = boston)
partial(boston.rf, pred.var = c("lstat", "rm"), convex.hull = TRUE, plot = TRUE)
\end{example}
